### 2020-01-25 conclusions.tex
Tiny fix

As future work, we would like to further validate our approach and
improve our admittedly \emph{ad hoc} mutant distance metric.  Allowing
user feedback \cite{EndUserMistake,OnlyOracle}, or applying metric
learning methods \cite{kulis2012metric} (particularly unsupervised
learning \cite{scholkopf1998nonlinear,tipping1999probabilistic}) are
the most obvious and interesting possibilities for a better metric.
Finally, mutant prioritization should be applicable to improving
software testing, as well \cite{groce2018verified}.

>>>>

As future work, we would like to further validate our approach and
improve our admittedly \emph{ad hoc} mutant distance metric.  Allowing
user feedback \cite{EndUserMistake,OnlyOracle}, or applying metric
learning methods \cite{kulis2012metric} (particularly unsupervised
learning \cite{scholkopf1998nonlinear,tipping1999probabilistic}) are
the most obvious and interesting possibilities for a better metric.
Finally, mutant prioritization should be applicable to improving
software testing, as well \cite{groce2018verified}.  We are also interested in combining static analysis and testing mutation analysis: it might be useful to consider a mutant killed if it is detected either by static or dynamic analysis, using static kills to lower the number of required costly testing/verification runs for mutants and the combined result as a useful guide to the quality of overall \emph{defense in depth} for high-importance code.
